A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2020-06-22 03_Prep_data.Rmd
Dose factor complicates the model, therefore it will be removed and tested as a random factor later

Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`. 
We will retain dose in the trial factor.

```{r}
slimmer_PM_dat <- slimmer_PM_dat[,colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
```

>>>>

Using the model without dose produces a lower AIC, however we should accept the data with dose as there is a significant difference between the models and we should accept the more complicated model `m2`. 
We will try and evaluate dose in the meta-analysis, however for now we will remove the dose factor to reduce the possibility of overfitting the model.

```{r}
slimmer_PM_dat$trial <- slimmer_PM_dat$trial_noDose
slimmer_PM_dat <- slimmer_PM_dat[,colnames(slimmer_PM_dat) != "trial_noDose"] #remove second trial column
write.csv(slimmer_PM_dat, file = "cache/slimmer_PM_clusterdat.csv", row.names = FALSE)
```
